LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2022-08-04 src/tex/ms.tex
update arXiv references

We note that \lw{} is not the only initiative of this kind. We highlight the ``Gravitational Wave Universe Toolbox'' presented by \citet{Yi2021} which was developed to simulate observations on the GW universe with different detectors covering the full gravitational-wave spectrum and source classes. We also highlight ``GWPlotter'' by \citep{Moore+2015}, which provides an interactive plotting tool to compare the sensitivity of different gravitational wave detectors. \lw{} differs from the tools listed here as we have tried to provide tools that are optimised to rapidly make predictions for large populations of stellar-origin sources and we have focused on space-based detectors.

>>>>

We note that \lw{} is not the only initiative of this kind. We highlight the ``Gravitational Wave Universe Toolbox'' presented by \citet{Yi+2022} which was developed to simulate observations on the GW universe with different detectors covering the full gravitational-wave spectrum and source classes. We also highlight ``GWPlotter'' by \citep{Moore+2015}, which provides an interactive plotting tool to compare the sensitivity of different gravitational wave detectors. \lw{} differs from the tools listed here as we have tried to provide tools that are optimised to rapidly make predictions for large populations of stellar-origin sources and we have focused on space-based detectors.
